\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[utf8]{inputenc}
\usepackage{parskip}

% Formatting titles
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}
\titlespacing{\subsection}{0pt}{8pt}{4pt}

% Custom command for list items
\newcommand{\cvitem}[2]{\item \textbf{#1} \hfill #2}
\newcommand{\publication}[4]{\item \textbf{#1}. #2. \textit{#3}. #4}

\begin{document}

\begin{center}
    {\Huge \textbf{Yang Zhou}} \\[4pt]
    \textbf{Ph.D. Student, Rutgers University -- Department of Computer Science} \\[4pt]
    \href{mailto:eta.yang@rutgers.edu}{eta.yang@rutgers.edu} $|$ +1 732 558 9675 \\[4pt]
    \href{https://etayang10th.github.io/}{Personal Website} $|$
    \href{https://www.linkedin.com/in/yang-zhou-0b6a78293/}{LinkedIn} $|$
    \href{https://scholar.google.com/citations?user=BsQ8IUcAAAAJ&hl=en}{Google Scholar} $|$
    \href{https://github.com/EtaYang10th}{GitHub} $|$
    \href{https://huggingface.co/EtaYang10th}{Hugging Face}
\end{center}

\section{Education}
\begin{itemize}[leftmargin=*, label={}]
    \item \textbf{Rutgers University} \hfill September 2023 -- Present \\
    Ph.D. in Computer Science \\
    Specialization: Large Language Models, Computer Vision

    \item \textbf{University of Science and Technology of China} \hfill September 2020 -- June 2023 \\
    Master of Engineering, Control Science and Engineering \\
    Specialization: Computer Vision, Object Detection, CNN Architecture

    \item \textbf{Southwest University} \hfill September 2016 -- June 2020 \\
    Bachelor of Engineering, Automation \\
    Specialization: Signals \& Systems
\end{itemize}

\section{Publications}

\subsection*{MLLM, LLM, MCP \& Multi-Agent}
\begin{itemize}[leftmargin=*, label={\textbullet}]
    \item \href{https://arxiv.org/abs/2511.17729}{\textbf{M3-Bench: Multi-Modal, Multi-Hop, Multi-Threaded Tool-Using MLLM Agent Benchmark}} \\
    \textbf{Yang Zhou}, Mingyu Zhao, Zhenting Wang, Difei Gu, Bangwei Guo, Ruosong Ye, Ligong Han, Can Jin, Dimitris N. Metaxas. \\
    \textit{arXiv}, Submitted on 21 Nov 2025.

    \item \href{https://arxiv.org/abs/2503.13794}{\textbf{LED: LLM Enhanced Open-Vocabulary Object Detection without Human Curated Data Generation}} \\
    \textbf{Yang Zhou}, Shiyu Zhao, Yuxiao Chen, Zhengting Wang, Dimitris N. Metaxas. \\
    \textit{arXiv}, OpenReview Submitted.

    \item \href{https://arxiv.org/pdf/2504.09772}{\textbf{Your Reward Function for RL is Your Best PRM for Search: Unifying RL and Search-Based TTS}} \\
    Can Jin, \textbf{Yang Zhou}, Qixin Zhang, Hongwu Peng, Di Zhang, Marco Pavone, Ligong Han, Zhang-Wei Hong, Tong Che, Dimitris N. Metaxas. \\
    \textit{arXiv}, OpenReview Submitted.
\end{itemize}

\subsection*{Computer Vision}
\begin{itemize}[leftmargin=*, label={\textbullet}]
    \item \href{https://aclanthology.org/2024.signlang-1.45/}{\textbf{A Multimodal Spatio-Temporal GCN Model with Enhancements for Isolated Sign Recognition}} \\
    \textbf{Yang Zhou}, Zhaoyang Xia, Yuxiao Chen, Carol Neidle, Dimitris N. Metaxas. \\
    \textit{LREC-COLING 2024}.

    \item \href{https://link.springer.com/article/10.1007/s10462-022-10213-5}{\textbf{A Review of Convolutional Neural Network Architectures and Their Optimizations}} \\
    Shuang Cong, \textbf{Yang Zhou}. \\
    \textit{Artificial Intelligence Review} (IF 9.588/Q1).

    \item \href{https://aclanthology.org/2024.signlang-1.44/}{\textbf{Diffusion Models for Sign Language Video Anonymization}} \\
    Zhaoyang Xia, \textbf{Yang Zhou}, Ligong Han, Carol Neidle, Dimitris N. Metaxas. \\
    \textit{LREC-COLING 2024}.
\end{itemize}

\subsection*{Previous Work (Modeling, Data Analysis, Signals \& Systems)}
\begin{itemize}[leftmargin=*, label={\textbullet}]
    \item \href{https://onlinelibrary.wiley.com/doi/epdf/10.1155/2019/6585102}{\textbf{A Multistory Building Evacuation Model Based on Multiple-Factor Analysis}} \\
    \textbf{Yang Zhou}, Zichuan Fan. \\
    \textit{Advances in Civil Engineering} (IF 1.924/Q3).

    \item \href{https://www.sciencedirect.com/science/article/pii/S0263224120314317}{\textbf{The Excitation and Detection of Lamb Waves in a Droplet-Loaded Plate Using Air-Coupled Ultrasonic Transducers}} \\
    Zichuan Fan, \textbf{Yang Zhou}, Tanghong Wu. \\
    \textit{Measurement} (IF 5.131/Q1).

    \item \href{https://www.sciencedirect.com/science/article/pii/S0263224119307924}{\textbf{Quasi-Dispersion of Air-Coupled Ultrasonic Signal for Angle-Dependent Reception}} \\
    Zichuan Fan, \textbf{Yang Zhou}, Tianhao Qie. \\
    \textit{Measurement} (IF 5.131/Q1).

    \item \href{https://ieeexplore.ieee.org/document/8813503}{\textbf{Multiphysics Model of Lamb Waves Propagation in a Plate Loaded with Droplets}} \\
    \textbf{Yang Zhou}, Zichuan Fan. \\
    \textit{ICCAR 2019, IEEE}.

    \item \href{https://www.sciencedirect.com/science/article/pii/S0263224119303094}{\textbf{Multiple Reflective Signal Reception in Gas Flow Measurement Using Air-Coupled Leaky Lamb Waves}} \\
    Zichuan Fan, Tianhao Qie, \textbf{Yang Zhou}. \\
    \textit{Measurement} (IF 5.131/Q1).
\end{itemize}

\section{Teaching \& Talks}
\begin{itemize}[leftmargin=*, label={}]
    \item \textbf{Computer Security} (Teaching Assistant) \hfill Spring 2025 \\
    Rutgers University, New Jersey, USA

    \item \textbf{Systems Programming} (Teaching Assistant) \hfill Fall 2023, Spring 2024 \\
    Rutgers University, New Jersey, USA

    \item \textbf{Neural Networks and Deep Learning} (Teaching Assistant) \hfill Aug 2021 \\
    University of Science and Technology of China, Hefei, China

    \item \textbf{Characteristics of Lamb Waves and Their Leakage Waves} (Presenter) \hfill May 2019 \\
    ICCAR International Academic Conference, Beijing, China
\end{itemize}

\section{Skills}
\begin{itemize}[leftmargin=*, label={\textbullet}]
    \item \textbf{Operating Systems:} Windows, Linux
    \item \textbf{Programming:} Python (primary), C++, Java
    \item \textbf{Tools:} Office Suite, MATLAB
\end{itemize}

\section{Honors \& Patents}
\begin{itemize}[leftmargin=*, label={\textbullet}]
    \item 2019 Invention Patents (China)
    \item 2019 Utility Model Patent (China)
    \item 2019 Mathematical Contest in Modeling (COMAP) -- Meritorious Winner
\end{itemize}

\end{document}
